---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load package and prepare input, the input is a list contains two, three or four vectors.

```{r}
library(freeVenn)
set.seed(123)  # Set the seed to ensures reproducibility

vlist <- list(
  groupA=sample(1:100, 80), 
  groupB=sample(50:150, 70), 
  groupC=sample(1:100, 60)
)

```

You can make standard (unweighted) Venn diagram with default setting.

```{r}
freeVenn(vlist)
```

By setting `weighted=TRUE` to make weighted Venn diagram in which the sizes of the regions are proportional to their corresponding values.

The `freeVenn` function returns a ggplot2 object, this makes it easy to customize the plot, for example, you can specify different colors using ggplot2 grammars.

```{r}
freeVenn(vlist, weighted=TRUE, color=c('red', 'green', 'blue'), fontface='bold') + 
  scale_fill_manual(values=c('#ff70a6', '#70d6ff', '#ffd670'))

```

It works for a list with four sets.
```{r}
vlist4 <- list(groupA=sample(1:100, 80), groupB=sample(50:150, 70), groupC=sample(1:100, 60), groupD=sample(50:150, 70))

freeVenn(vlist4)
```

It works for list with two sets.

```{r}
vlist2 <- list(groupA=sample(1:100, 80), groupB=sample(50:150, 30))

freeVenn(vlist2, weighted=TRUE)
```
```{r}
freeVenn(vlist, radii=0.8)
```

```{r}
freeVenn(vlist, radii=1.5)
```
